---
title: "Final Project"
author: "ash r"
format: html
page-layout: full
theme: lux
editor: visual
---

# Loading Relevant Packages

```{r load-packages}
#| message: false
library(tidyverse)
library(knitr)
library(ggformula)
library(GGally)
library(dplyr)
library(mosaic)
library(broom)
library(RColorBrewer)
```

# Loading the Data Set

```{r load-data}
finance_data <- read.csv("data/NFWBS_PUF_2016_data.csv")
```

# Creating a New Data Frame with Relevant Variables

```{r new-df}
finance <- data.frame(
  spending_habit = finance_data$FS1_6,
  consult_budget = finance_data$PROPPLAN_1,
  frugality = finance_data$FRUGALITY,
  materialism = finance_data$MATERIALISM_3,
  impulsive = finance_data$SELFCONTROL_1,
  resist_temptation = finance_data$SELFCONTROL_2,
  age_group = finance_data$agecat
)
```

The result:

```{r glimpse-data}
glimpse(finance)
```

# Data Dictionary

The following are responses from the survey, along with their scales of measurement.

[Response variable(s):]{.underline}

-   `spending_habit`: "I know how to keep myself from spending too much." (1-5)
    -   1: Not at all
    -   2: Very little
    -   3: Somewhat
    -   4: Very well
    -   5: Completely

[Explanatory variable(s):]{.underline}

-   `consult_budget`: "I consult my budget to see how much I have left." (1-5)

    -   1: Strongly disagree

    -   2: Disagree

    -   3: Neither agree nor disagree

    -   4: Agree

    -   5: Strongly agree

-   `frugality`: "If I can re-use an item I already have, there's no sense in buying something new." (1-6)

    -   1: Strongly disagree

    -   2: Disagree

    -   3: Disagree slightly

    -   4: Agree slightly

    -   5: Agree

    -   6: Strongly agree

-   `materialism`: "I like to own things that impress people." (1-5)

    -   1: Strongly disagree

    -   2: Disagree

    -   3: Neither agree nor disagree

    -   4: Agree

    -   5: Strongly agree

-   `impulsive`: "I often act without thinking through all the alternatives." (1-4)

    -   1: Not at all

    -   2: Not very well

    -   3: Very well

    -   4: Completely well

-   `resist_temptation`: "I am good at resisting temptation." (1-4)

    -   1: Not at all

    -   2: Not very well

    -   3: Very well

    -   4: Completely well

[Demographic data (could also be explanatory):]{.underline}

-   `age_group`: Respondent age, grouped into categories:
    -   1: 18-24
    -   2: 25-34
    -   3: 35-44
    -   4: 45-54
    -   5: 55-61
    -   6: 62-69
    -   7: 70-74
    -   8: 75+

# Cleaning the Data

The following variables include a score of -1 to indicate that the respondent refused to answer: `spending_habit`, `frugality`, `materialism`, `impulsive`, `resist_temptation`.

That is not helpful in this instance, so I removed all observations with that score. Note that, per the official data dictionary provided by the CFPB (<https://files.consumerfinance.gov/f/documents/cfpb_nfwbs-puf-codebook.pdf>), there were no (relevant) observations that included the number 0.

```{r remove-negative}
#I filtered the data frame to only include observations that are not -1.
finance <- finance |>
  filter(spending_habit != -1,
         frugality != -1,
         materialism != -1,
         impulsive != -1,
         resist_temptation != -1)
```

There are now 6194 observations left from the initial 6394 observations.

Since `age_group` has the ages grouped into categories ranging from 1-8, I decided to use it as a categorical variable. To make things easier, I renamed the categories to reflect the age range being represented.

```{r rename-age}
finance <- finance |>
 mutate(age_group = case_when(
   age_group == 1 ~ "18-24",
   age_group == 2 ~ "25-34",
   age_group == 3 ~ "35-44",
   age_group == 4 ~ "45-54",
   age_group == 5 ~ "55-61",
   age_group == 6 ~ "62-69",
   age_group == 7 ~ "70-74",
   age_group == 8 ~ "75+"
 ))
```

Lastly, since these are categorical variables, I factored them so that they can be used as such.

Note: Later, I will be using a logistic regression model. I kept the original spending habit variable and added a factored one and a binary one. Since that variable is measured on a scale of 1-5, going from negative to positive, responses ranging from 1-3 were grouped as 0, and #responses 4 and 5 were grouped as 1. Including 3, which is neutral, in group 0 was an analytical decision.

```{r factoring}
finance <- finance |>
  mutate(
    spending_habit_original = spending_habit,
    spending_habit = factor(spending_habit),
    spending_binary = if_else(spending_habit_original >= 4, 1, 0),
    consult_budget = factor(consult_budget),
    frugality = factor(frugality),
    materialism = factor(materialism),
    impulsive = factor(impulsive),
    resist_temptation = factor(resist_temptation),
    age_group = factor(age_group)
  )
```

------------------------------------------------------------------------

The result:

```{r preview-data}
kable(head(finance))
```

# Univariate Plots

```{r new_colour}
#I wanted to use a specific colour, so I assigned its hex code to a variable.
special_purple <- "#412d5e"
```

------------------------------------------------------------------------

## Spending Habits, Consulting a Budget:

```{r spending-and-budget-bars}
spending_bar <- gf_bar( ~ spending_habit, data = finance, fill = special_purple) |> 
  gf_labs(x = "Scores (Ranging From 'Not At All' to 'Completely')",
          y = "Number of Respondents",
          title = "Distribution of Responses about Spending Habits",
          caption = "Prompt: 'I know how to keep myself from spending too much.'") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, size = 12),
        plot.title = element_text(size = 16))
#---------------------------------------------------------------------------
budget_bar <- gf_bar( ~ consult_budget, data = finance, fill = special_purple) |> 
  gf_labs(x = "Scores (Ranging from 'Strongly Disagree' to 'Strongly Agree')",
          y = "Number of Respondents",
          title = "Distribution of Responses about Consulting a Budget",
          caption = "Prompt: 'I consult my budget to see how much I have left.'") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, size = 12),
        plot.title = element_text(size = 16))
```

------------------------------------------------------------------------

```{r displaying-spending-and-budget-bars}
#| layout-ncol: 2

spending_bar
budget_bar
```

------------------------------------------------------------------------

## Frugality, Materialism:

```{r frugality-and-materialism-bars}
frugality_bar <- gf_bar( ~ frugality, data = finance, fill = special_purple) |> 
  gf_labs(x = "Scores (Ranging from 'Strongly Disagree' to 'Strongly Agree')",
          y = "Number of Respondents",
          title = "Distribution of Responses about Frugality",
          caption = "Prompt: 'If I can reuse an item I already have, there's no sense in buying \nsomething new.'") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, size = 12),
        plot.title = element_text(size = 16))
#---------------------------------------------------------------------------
materialism_bar <- gf_bar( ~ materialism, data = finance, fill = special_purple) |> 
  gf_labs(x = "Scores (Ranging from 'Strongly Disagree' to 'Strongly Agree')",
          y = "Number of Respondents",
          title = "Distribution of Responses about Materialism",
          caption = "Prompt: 'I like to own things that impress people.'") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, size = 12),
        plot.title = element_text(size = 16))
```

------------------------------------------------------------------------

```{r displaying-frugality-and-materialism-bars}
#| layout-ncol: 2

frugality_bar
materialism_bar
```

------------------------------------------------------------------------

## Impulsivity, Temptation:

```{r impulsive-and-temptation-bars}
impulsive_bar <- gf_bar( ~ impulsive, data = finance, fill = special_purple) |> 
  gf_labs(x = "Scores (Ranging from 'Not At All' to 'Completely Well')",
          y = "Number of Respondents",
          title = "Distribution of Responses about Impulsivity",
          caption = "Prompt: 'I often act without thinking through all the alternatives.'") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, size = 12),
        plot.title = element_text(size = 16))
#---------------------------------------------------------------------------
temptation_bar <- gf_bar( ~ resist_temptation, data = finance, fill = special_purple) |> 
  gf_labs(x = "Scores (Ranging from 'Not At All' to 'Completely Well')",
          y = "Number of Respondents",
          title = "Distribution of Responses about Resisting Temptation",
          caption = "Prompt: 'I am good at resisting temptation.'") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, size = 12),
        plot.title = element_text(size = 16))
```

------------------------------------------------------------------------

```{r displaying-impulsive-and-temptation-bars}
#| layout-ncol: 2

impulsive_bar
temptation_bar
```

------------------------------------------------------------------------

## Age:

```{r age-bar}
age_group_bar <- gf_bar( ~ age_group, data = finance, fill = special_purple) |> 
  gf_labs(x = "Age Groups",
          y = "Number of Respondents",
          title = "Distribution of Respondent Ages") + 
  theme_minimal() +
  theme(plot.title = element_text(size = 16))
```

------------------------------------------------------------------------

```{r displaying-age-bars}
#| fig-align: "center"

age_group_bar
```

# Bivariate Plots

```{r new-purple-palette}
# The lightest color for my desired palette is too light, so I'm modifying it to skip it
purple_palette <- brewer.pal(7, "Purples")[3:7]
```

## Spending Habits & Consulting a Budget:

```{r spending-consult-budget-bar-tally}
spending_budget_bar <- gf_bar(~ consult_budget, data = finance, fill = ~ spending_habit, position = "fill") |>
  gf_labs(x = "Scores (Consulting a Budget)",
          y = "Proportion of Respondents",
          title = "Spending Habits & Consulting a Budget",
          subtitle = "'I know how to keep myself from spending too much' & 'I consult my budget to see how much I have left.'",
          caption = "* 'Spending Habits' scores range from 'not at all' (1) to 'completely' (5) \n* 'Consulting a Budget' scores range from 'strongly disagree' (1) to 'strongly agree' (5)",
          fill = "Scores \n(Spending \nHabits)") +
  theme_minimal() +
  scale_fill_manual(values = purple_palette) +
  theme(plot.subtitle = element_text(size = 9.8),
        plot.caption = element_text(hjust = 0, size = 10))
#---------------------------------------------------------------------------
spending_budget_tally <- tally(spending_habit ~ consult_budget, data = finance)
```

------------------------------------------------------------------------

```{r displaying-spending-consult-budget-bar-tally}
#| layout-ncol: 2

spending_budget_bar
spending_budget_tally
```

------------------------------------------------------------------------

## Spending Habits & Frugality:

```{r spending-frugality-bar-tally}
spending_frugality_bar <- gf_bar(~ frugality, data = finance, fill = ~ spending_habit, position = "fill") |>
  gf_labs(x = "Scores (Frugality)",
          y = "Proportion of Respondents",
          title = "Spending Habits & Frugality",
          subtitle = "'I know how to keep myself from spending too much' & 'If I can reuse an item I already have, there's \nno sense in buying something new.'",
          caption = "* 'Spending Habits' scores range from 'not at all' (1) to 'completely' (5) \n* 'Frugality' scores range from 'strongly disagree' (1) to 'strongly agree' (5)",
          fill = "Scores \n(Spending \nHabits)") +
  theme_minimal() +
  scale_fill_manual(values = purple_palette) +
  theme(plot.subtitle = element_text(size = 10),
        plot.caption = element_text(hjust = 0, size = 10))
#---------------------------------------------------------------------------
spending_frugality_tally <- tally(spending_habit ~ frugality, data = finance)
```

------------------------------------------------------------------------

```{r displaying-spending-frugality-bar-tally}
#| layout-ncol: 2

spending_frugality_bar
spending_frugality_tally
```

------------------------------------------------------------------------

## Spending Habits & Materialism:

```{r spending-materialism-bar-tally}
spending_materialism_bar <- gf_bar(~ materialism, data = finance, fill = ~ spending_habit, position = "fill") |>
  gf_labs(x = "Scores (Materialism)",
          y = "Proportion of Respondents",
          title = "Spending Habits & Materialism",
          subtitle = "'I know how to keep myself from spending too much' & 'I like to own things that impress people'",
          caption = "* 'Spending Habits' scores range from 'not at all' (1) to 'completely' (5) \n* 'Materialism' scores range from 'strongly disagree' (1) to 'strongly agree' (5)",
          fill = "Scores \n(Spending \nHabits)") +
  theme_minimal() +
  scale_fill_manual(values = purple_palette) +
  theme(plot.subtitle = element_text(size = 10.5),
        plot.caption = element_text(hjust = 0, size = 10))
#---------------------------------------------------------------------------
spending_materialism_tally <- tally(spending_habit ~ materialism, data = finance) 
```

------------------------------------------------------------------------

```{r displaying-materialism-bar-tally}
#| layout-ncol: 2

spending_materialism_bar
spending_materialism_tally
```

------------------------------------------------------------------------

## Spending Habits & Impulsivity:

```{r spending-impulsive-bar-tally}
spending_impulsive_bar <- gf_bar(~ impulsive, data = finance, fill = ~ spending_habit, position = "fill") |>
  gf_labs(x = "Scores (Impulsivity)",
          y = "Proportion of Respondents",
          title = "Spending Habits & Impulsivity",
          subtitle = "'I know how to keep myself from spending too much' & 'I often act without thinking \nthrough all the alternatives'",
          caption = "* 'Spending Habits' scores range from 'not at all' (1) to 'completely' (5) \n* 'Impulsivity' scores range from 'not at all' (1) to 'completely well' (4)",
          fill = "Scores \n(Spending \nHabits)") +
  theme_minimal() +
  scale_fill_manual(values = purple_palette) +
  theme(plot.subtitle = element_text(size = 11),
        plot.caption = element_text(hjust = 0, size = 10))
#---------------------------------------------------------------------------
spending_impulsive_tally <- tally(spending_habit ~ impulsive, data = finance)
```

------------------------------------------------------------------------

```{r displaying-spending-impulsive-bar-tally}
#| layout-ncol: 2

spending_impulsive_bar
spending_impulsive_tally
```

------------------------------------------------------------------------

## Spending Habits & Resisting Temptation:

```{r spending-temptation-bar-tally}
spending_temptation_bar <- gf_bar(~ resist_temptation, data = finance, fill = ~ spending_habit, position = "fill") |>
  gf_labs(x = "Scores (Resisting Temptation)",
          y = "Proportion of Respondents",
          title = "Spending Habits & Resisting Temptation",
          subtitle = "'I know how to keep myself from spending too much' & 'I am good at resisting temptation.'",
          caption = "* 'Spending Habits' scores range from 'not at all' (1) to 'completely' (5) \n* 'Resisting Temptation' scores range from 'not at all' (1) to 'completely well' (4)",
          fill = "Scores \n(Spending \nHabits)") +
  theme_minimal() +
  scale_fill_manual(values = purple_palette) +
  theme(plot.subtitle = element_text(size = 11),
        plot.caption = element_text(hjust = 0, size = 10))
#---------------------------------------------------------------------------
spending_temptation_tally <- tally(spending_habit ~ resist_temptation, data = finance)
```

------------------------------------------------------------------------

```{r displaying-spending-temptation-bar-tally}
#| layout-ncol: 2

spending_temptation_bar
spending_temptation_tally
```

------------------------------------------------------------------------

## Spending Habits & Age:

```{r spending-age-bar-tally}
spending_age_bar <- gf_bar(~ age_group, data = finance, fill = ~ spending_habit, position = "fill") |>
  gf_labs(x = "Age Groups",
          y = "Proportion of Respondents",
          title = "Spending Habits & Age",
          subtitle = "'I know how to keep myself from spending too much' & respondent ages",
          caption = "* 'Spending Habits' scores range from 'not at all' (1) to 'completely' (5)",
          fill = "Scores \n(Spending \nHabits)") +
  theme_minimal() +
  scale_fill_manual(values = purple_palette) +
  theme(plot.subtitle = element_text(size = 11),
        plot.caption = element_text(hjust = 0, size = 10))
#---------------------------------------------------------------------------
spending_age_tally <- tally(spending_habit ~ age_group, data = finance)
```

------------------------------------------------------------------------

```{r displaying-spending-age-bar-tally}
#| layout-ncol: 2

spending_age_bar
spending_age_tally
```

------------------------------------------------------------------------

# Summaries

```{r generalised-pairs-plot}
#| warning: false
#| fig-height: 23
#| fig-width: 23
ggpairs(finance)
```

# Adjustments & New Plots

I decided to narrow my scope to young adults (ages 18-24). This reduced my number of observations to 396 (from 6195).

```{r filtering-age}
young_adult <- finance |> filter(age_group == "18-24")
```

------------------------------------------------------------------------

## Univariate: Spending Habits

```{r ya-spending-bar}
ya_spending_bar <- gf_bar( ~ spending_habit, data = young_adult, fill = "darkseagreen4") |> 
  gf_labs(x = "Scores (Ranging From 'Not At All' to 'Completely')",
          y = "Number of Respondents",
          title = "Distribution of Responses about Spending Habits in Young Adults (18-24)",
          caption = "Prompt: 'I know how to keep myself from spending too much.'") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, size = 12),
        plot.title = element_text(size = 16))
```

------------------------------------------------------------------------

```{r displaying-ya-spending-bar}
#| fig-align: "center"

ya_spending_bar
```

------------------------------------------------------------------------

```{r new-green-palette}
# The lightest color for my desired palette is too light, so I'm modifying it to skip it
green_palette <- brewer.pal(7, "Greens")[3:7]
```

------------------------------------------------------------------------

## Bivariate: Spending Habits & Materialism

```{r ya-spending-materialism-plots}
ya_spending_materialism_bar <- gf_bar(~ materialism, data = young_adult, fill = ~ spending_habit, position = "fill") |>
  gf_labs(x = "Scores (Materialism)",
          y = "Proportion of Respondents",
          title = "Spending Habits & Materialism in Young Adults (18-24)",
          subtitle = "'I know how to keep myself from spending too much' & 'I like to own things that impress people'",
          caption = "* 'Spending Habits' scores range from 'not at all' (1) to 'completely' (5) \n* 'Materialism' scores range from 'strongly disagree' (1) to 'strongly agree' (5)",
          fill = "Scores \n(Spending \nHabits)") +
  theme_minimal() +
  scale_fill_manual(values = green_palette) +
  theme(plot.subtitle = element_text(size = 10.5),
        plot.caption = element_text(hjust = 0, size = 10))
#---------------------------------------------------------------------------
ya_spending_materialism_jitter <- young_adult |> 
  gf_jitter(spending_binary ~ materialism, color = ~ materialism) |>
  gf_labs(x = "Scores (Materialism)",
          y = "Spending Habits",
          title = "Spending Habits & Materialism in Young Adults (18-24)",
          subtitle = "'I know how to keep myself from spending too much' & 'I like to own things that impress people'",
          caption = "* 'Spending Habits' have two categories — 'Undesirable' (0) and 'Desirable' (1) \n* 'Materialism' scores range from 'strongly disagree' (1) to 'strongly agree' (5)",
          color = "Scores (Materialism)") +
  theme_minimal() +
  scale_color_manual(values = green_palette) +
  theme(plot.subtitle = element_text(size = 11),
        plot.caption = element_text(hjust = 0, size = 10))
#---------------------------------------------------------------------------
ya_spending_materialism_tally <- tally(spending_habit ~ materialism, data = young_adult)
```

------------------------------------------------------------------------

```{r displaying-ya-spending-materialism-jitter-tally}
#| layout-ncol: 2

ya_spending_materialism_jitter
ya_spending_materialism_tally
```

------------------------------------------------------------------------

## Bivariate: Spending Habits & Impulsivity

```{r ya-spending-impulsive-plots}
ya_spending_impulsive_bar <- gf_bar(~ impulsive, data = young_adult, fill = ~ spending_habit, position = "fill") |>
  gf_labs(x = "Scores (Impulsivity)",
          y = "Proportion of Respondents",
          title = "Spending Habits & Impulsivity in Young Adults (18-24)",
          subtitle = "'I know how to keep myself from spending too much' & 'I often act without thinking \nthrough all the alternatives'",
          caption = "* 'Spending Habits' scores range from 'not at all' (1) to 'completely' (5) \n* 'Impulsivity' scores range from 'not at all' (1) to 'completely well' (4)",
          fill = "Scores \n(Spending \nHabits)") +
  theme_minimal() +
  scale_fill_manual(values = green_palette) +
  theme(plot.subtitle = element_text(size = 11),
        plot.caption = element_text(hjust = 0, size = 10))
#---------------------------------------------------------------------------
ya_spending_impulsive_jitter <- young_adult |> 
  gf_jitter(spending_binary ~ impulsive, color = ~ impulsive) |>
  gf_labs(x = "Scores (Impulsivity)",
          y = "Spending Habits",
          title = "Spending Habits & Impulsivity in Young Adults (18-24)",
          subtitle = "'I know how to keep myself from spending too much' & 'I often act without thinking \nthrough all the alternatives'",
          caption = "* 'Spending Habits' have two categories — 'Undesirable' (0) and 'Desirable' (1) \n* 'Impulsivity' scores range from 'not at all' (1) to 'completely well' (4)",
          color = "Scores (Impulsivity)") +
  theme_minimal() +
  scale_color_manual(values = green_palette) +
  theme(plot.subtitle = element_text(size = 11),
        plot.caption = element_text(hjust = 0, size = 10))
#---------------------------------------------------------------------------
ya_spending_impulsive_tally <- tally(spending_habit ~ impulsive, data = young_adult)
```

------------------------------------------------------------------------

```{r displaying-ya-spending-impulsive-jitter-tally}
#| layout-ncol: 2

ya_spending_impulsive_jitter
ya_spending_impulsive_tally
```

# Comparisons

## Spending Habits in Total Sample vs Young Adults:

```{r displaying-spending-bar-total-ya}
#| layout-ncol: 2

spending_bar
ya_spending_bar
```

------------------------------------------------------------------------

## Spending Habits & Materialism in Total Sample vs Young Adults:

```{r displaying-spending-materialism-bar-total-ya}
#| layout-ncol: 2

spending_materialism_bar
ya_spending_materialism_bar
```

------------------------------------------------------------------------

## Spending Habits & Impulsivity in Total Sample vs Young Adults:

```{r displaying-spending-impulsive-bar-total-ya}
#| layout-ncol: 2

spending_impulsive_bar
ya_spending_impulsive_bar
```

# Regression Models

## Making the Models

### Model 1: Using Materalism to Predict Spending Habits in Young Adults

```{r materialism_model}
materialism_fit <- glm(spending_binary ~ materialism, data = young_adult, family = "binomial")
tidy(materialism_fit, conf.int = TRUE, conf.level = 0.95) |> kable()

glance(materialism_fit) |>
  dplyr::select(AIC, BIC) |> kable()
```

### Model 2: Using Impulsivity to Predict Spending Habits in Young Adults

```{r impulsive-fit-model}
impulsive_fit <- glm(spending_binary ~ impulsive, data = young_adult, family = "binomial")
tidy(impulsive_fit, conf.int = TRUE, conf.level = 0.95) |> kable()

glance(impulsive_fit) |>
  dplyr::select(AIC, BIC) |> kable()
```

### Model 3: Using Materialism & Impulsivity to Predict Spending Habits in Young Adults

```{r add-both-predictors-model}
add_fit <- glm(spending_binary ~ materialism + impulsive, data = young_adult, family = "binomial")
tidy(add_fit, conf.int = TRUE, conf.level = 0.95) |> kable()

glance(add_fit) |>
  dplyr::select(AIC, BIC) |> kable()
```

### Model 4: Using Materialism & Impulsivity AND Their Interaction to Predict Spending Habits in Young Adults

```{r interaction-model}
interact_fit <- glm(spending_binary ~ materialism + impulsive + materialism * impulsive,
                    data = young_adult, family = "binomial")
tidy(interact_fit) |> kable()

glance(interact_fit) |>
  dplyr::select(AIC, BIC) |> kable()
```

------------------------------------------------------------------------

## Comparing the Models to Determine the "Best" One

| Model          | Statistically Significant P-Values | AIC | BIC |
|----------------|------------------------------------|-----|-----|
| 1: Materialism | 1/4                                | 545 | 565 |
| 2: Impulsivity | 3/3                                | 525 | 541 |
| 3: Add         | 4/7                                | 523 | 555 |
| 4: Interact    | 1/19                               | 536 | 615 |

Note: Here, a statistically significant p-value means one that is \< 0.05.

Based on the table above:

-   Model 3 is the "best" one based on AIC.

-   Model 2 is the "best" one based on BIC\*.

-   Model 2 is the "best" one based on how many of its p-values are statistically significant (100%).

Models 2 and 3 are the best ones, overall. An analytical decision was made here, which was to choose Model 3 as our main model. This is because this model has SOME credibility (see: AIC) and is most representative of our research question, whereas Model 2 only accounts for one of the two predictor variables.

-   What we can learn from Model 2, however, is that impulsivity plays a huge role here.

## Assumptions

Linearity

-   A logistic model doesn't assume a linear relationship between the dependent and independent variables.

    -   Note: Should I investigate the log odds using logit? Probably. Ask about that.

Randomness:

-   Met in both.

Independence:

-   Somewhat met in both.

------------------------------------------------------------------------

## Plot of Model 3:

```{r predicted-probability-plot}
#| warning: false

grid <- expand.grid(
  materialism = young_adult$materialism,
  impulsive = young_adult$impulsive
)

grid$predicted_prob <- predict(add_fit, newdata = grid, type = "response")

predicted_probability_plot <- ggplot(grid, aes(x = materialism, y = predicted_prob, color = impulsive, group = impulsive)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_color_manual(values = green_palette) +
  labs(
    title = "Predicted Probability of Good Spending Habits in Young Adults (18-24)",
    subtitles = "Based on Self-Reported Spending Habits Scores (Ranging from 'not at all (1) to 'completely' (5)",
    caption = "* 'Materialism' scores range from 'strongly disagree' (1) to 'strongly agree' (5) \n* 'Impulsivity' scores range from 'not at all' (1) to 'completely well' (4)",
    x = "Materialism Scale",
    y = "Predicted Probability",
    color = "Impulsivity Scale"
  ) + 
  theme_minimal() +
  theme(plot.subtitle = element_text(size = 9),
        plot.caption = element_text(hjust = 0, size = 10))
```

```{r displaying-predicted-probability-plot}
#| fig-align: "center"
predicted_probability_plot
```

------------------------------------------------------------------------

# Final Thoughts

The results from the graph above show that self control and materialism do affect people's spending habits, at least to some extent. Impulsivity plays a larger role than materialism (see: the gaps between the lines), which is also shown by our other models and their results.

As materialism and impulsivity increase, "good" spending behaviours decrease.

These results likely aren't generalisable, though. All of the variables are subjective and rely on people self-reporting. Answers aren't necessarily accurate.

Moreover, it is hard to measure spending habits in particular because of how ambiguous the variable is. People can know how to keep themselves from spending too much, but that doesn't exactly say whether or not they actually do so.

------------------------------------------------------------------------

# Summary of Environment

```{r displaying-metadata}
sessionInfo()
```
